### 2023-07-10 tesis_Ashish/Chapter4/chapter4.tex
update

\section{Datasets}

For studying 2018 PCC dataset, we have divided CMS luminosity data taking into seven periods: A, B, C, D1, D2, D3, and D4, as depicted in % 2018 CMS luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4
as shown in Fig. \ref{fig:period_bound}. During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
%vdM data is shown during period B corresponding to Fill 6868.
Run range for each period is shown in Table \ref{tab:period run ranges}.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/period_boundary.png}
\caption{%
   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data.
}
\label{fig:period_bound}
\end{figure}

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{}c@{\hspace{1cm}}p{5.5cm}p{5.5cm}@{}}
    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\
    2018A & \begin{tabular}{@{}p{5.5cm}@{}}/AlCaLumiPixels/Run2018A-AlCaPCCRandom-15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO, \\ /StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO\end{tabular} & /AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018B & /StreamALCALUMIPIXELSEXPRESS/Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018C & /StreamALCALUMIPIXELSEXPRESS/Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018D & /StreamALCALUMIPIXELSEXPRESS/Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO \\
  \end{tabular}
  \caption{Dataset Information}
  \label{tab:datasets}
\end{table}

\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}

%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}

@@

\item $15Apr2023_UL2018_315252_316062_PCCRandom_-v1$: This part represents the processing version, date, and run range of the dataset. "15Apr2023" is the date when this specific version of the dataset was created. "UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis. The numbers $"315252_316062"$ represent the range of run numbers included in the dataset. $"PCCRandom_"$ is a reference to the Pixel Cluster Counting method used for luminosity measurement and the random trigger. "v1" denotes the version number of this processed dataset.

@@

$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$

@@

$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$

@@

$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$

@@

The calibration of luminosity measurement by the CMS experiment in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV was performed during

@@

To measure the luminosity using the pixel cluster counting method, pixel detector is divided into modules, each consisting of a number of pixels arranged in a grid. The number of pixel clusters produced in each module per unit time is proportional to the instantaneous luminosity of the collider. To implement this method, the pixel detector is operated in an integrated mode, where the detector is read out at a fixed time interval called a "lumi section". During each lumi section, the number of pixel clusters produced in each module is recorded, the rate of number of pixel clusters and visible cross section is used to determine the instantaneous luminosity of the collider. CMS software (CMSSW) version $10{\_}2{\_}2$  and $10{\_}6{\_}30$ are used for reprocessing PCC data. Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section. Random trigger PCC dataset is reprocessed with new module vetolist to obtain afterglow corrections with improved module stability selections. Zero bias dataset is reprocessed after applying afterglow corrections using same module vetolist with more stringent selections on module stability to obtain PCC luminosity.

@@

\item CMSSW: The CMS Software (CMSSW) is a comprehensive software framework developed for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. CMSSW is used for the simulation, processing, and analysis of data collected by the CMS detector. It is designed to handle various tasks, from the generation of simulated events to the reconstruction of raw detector data, calibration, and high-level analysis. CMSSW is composed of several interconnected components and follows a modular architecture to promote flexibility, reusability, and maintainability. Some key aspects of CMSSW include, Event Data Model (EDM): The EDM serves as the foundation of CMSSW, defining the structure and organization of data objects, such as particle candidates, detector hits, and reconstructed vertices. It is designed to handle the storage, retrieval, and manipulation of these objects efficiently. The CMSSW framework is responsible for the management of software modules, the flow of data between modules, and the execution of the necessary tasks. It also handles the scheduling of tasks and the parallelization of processes, enabling efficient use of computing resources. Modules: CMSSW is built upon a collection of software modules, each responsible for a specific task, such as event generation, detector simulation, reconstruction, or analysis. These modules can be combined and customized to create a complete processing chain for a given use case. The software includes a detailed description of the CMS detector geometry, material properties, and readout electronics. This information is used during the simulation and reconstruction processes to accurately model the detector's response to particles. 
Simulation: CMSSW integrates several external tools and libraries, such as the GEANT4 toolkit, to simulate the passage of particles through the CMS detector. This includes the interactions of particles with the detector material, the production of secondary particles, and the generation of detector signals. Reconstruction: The reconstruction algorithms in CMSSW process the raw detector data, converting it into meaningful physics objects, such as tracks, calorimeter clusters, and particle candidates. These algorithms use a variety of techniques, including pattern recognition, clustering, and fitting, to extract the relevant information from the detector signals. CMSSW includes tools for the calibration of detector components and the alignment of the detector geometry. These tasks are crucial for ensuring the accurate reconstruction of physics objects and the extraction of meaningful results from the data. Analysis: The software provides a rich set of high-level analysis tools and libraries, enabling researchers to perform a wide range of physics analyses, from searches for new particles to precision measurements of Standard Model processes. Data storage and management: CMSSW uses the ROOT data format for the storage and management of data objects. ROOT is a powerful and flexible data storage and processing framework developed at CERN, which provides efficient data handling, advanced statistical analysis tools, and extensive data visualization capabilities.

@@

\item Brilcalc: The brilcalc tool is a software package designed to calculate and analyze luminosity data for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. Luminosity is a crucial parameter in high-energy physics experiments like CMS, as it measures the rate of collisions in a particle accelerator and directly affects the statistical significance of experimental results. Brilcalc serves as a command-line interface (CLI) tool, which allows users to extract, manipulate, and visualize luminosity data from the CMS experiment. It is built upon the BRIL (Beam Radiation Instrumentation and Luminosity) project, which is responsible for the development and maintenance of beam monitoring and luminosity measurement systems at the CMS experiment. Users can extract luminosity data for a specific data-taking period or data range from the CMS database. The data can be filtered by various criteria, such as run number, fill number, and data-taking conditions. Data manipulation: The tool offers the capability to process and manipulate the extracted luminosity data. Users can perform operations such as unit conversion, data scaling, and data normalization to make the data suitable for further analysis. Brilcalc allows users to perform basic statistical analyses on the luminosity data, such as calculating integrated luminosity, average luminosity, and instantaneous luminosity. These analyses help physicists understand the performance of the CMS detector and plan future data-taking strategies. The tool can generate plots and graphs to visualize the luminosity data, making it easier for researchers to interpret the results and identify trends or anomalies. Brilcalc is designed to be extensible, allowing users to develop custom plugins and scripts for advanced data analysis and visualization tasks.

\item CERN ROOT: The ROOT data analysis framework, developed by CERN, is widely used in high-energy physics experiments, including CMS. ROOT offers a rich set of tools for data processing, statistical analysis, and visualization. In the context of PCC luminosity measurement, ROOT is employed to analyze and process the output data from CMSSW, perform statistical analyses, and generate plots for data visualization.

@@

\item DASgoclient: The DASgoclient is a command-line interface for the CMS Data Aggregation System (DAS). It offers researchers an alternative method for accessing various CMS data services without using the web-based DAS interface. The DASgoclient allows users to query and retrieve data in a more scriptable and automated manner, making it an essential tool for managing datasets and streamlining the data retrieval process for PCC luminosity measurements.

@@

@@

\begin{itemize}
\item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.

@@

\item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis. Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurements.
\end{itemize}

By carefully analyzing the module weights and excluding the bad modules from the analysis, the instabilities in PCC luminosity measurements can be minimized. This process ensures that the data used for luminosity measurements are of high quality and can produce accurate results.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/Module_weight.png}
\caption{%
   Method to obtain module weights as a function of lumi section for categorizing good and bad modules. X profile of TH2F histogram (module PCC/total PCC per lumi section) is obtained. X profile is then filled in a TGraph after removing points with error $>$ 0.05. TGraph is normalized with the mean of Y projection of TH2F histogram to obtain module stability profile.
}
\label{fig:mod_weight}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules.png}
\caption{%
   Variation of normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large rms/mean values are used to make module vetolist.
}
\label{fig:goodbadmodules}
\end{figure}

Module vetolist is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,

@@

\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut} and \ref{fig:f_it}.

\item All barrel layer 1 modules are removed as these modules are significantly affected by dynamic inefficiency effects, where the hit efficiency decreases at higher $L_{inst}$ due to the readout chip not being able to process all of the hits.                                                                              
\item A loose selection of 7\% based on rms/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile. Modules with significantly large rms/mean are removed with this loose selection as shown in Fig. \ref{fig:outliermodules}.

\item Module stability is re-evaluated based on rms/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig. \ref{fig:sec_it_cut}.                                                      
\end{itemize}

@@

\item Period B module veto list is applied to these periods to determine remaining bad modules.

@@

\item module weight comparisons between period B and these periods is done and modules with more than 3 sigma change in module weights are removed as shown in Fig. \ref{fig:mod_w_com} and Fig \ref{fig:mod_w_com_1}.      .                                                                             
\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
\caption{%
 Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC is applied to remove low statistics lumi sections.
}
\label{fig:PCC_cut}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration.png}
\caption{%
   A loose cut of 7\% is applied on rms/mean values of module stability profile to remove outlier modules.
}
\label{fig:f_it}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/cut_selection.png}
\caption{%
   RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
}
\label{fig:outliermodules}
\end{figure}

>>>>

\section{Dataset}

For studying the performance of PCC luminometer during 2018 data taking, we have divided CMS luminosity data taking into seven periods: A, B, C, D1, D2, D3, and D4, as depicted in % 2018 CMS luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4
Fig. \ref{fig:period_bound}. Run ranges for each period are shown in Table \ref{tab:period_run_ranges}.
During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
%vdM data is shown during period B corresponding to Fill 6868.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/period_boundary.png}
\caption[2018 CMS luminosity data taking periods.]{%
   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}
    \textbf{Period}   & \textbf{Run range} \\ \hline
     2018A      &        315252-316995         \\
     2018B      &        317080-319311         \\
     2018C      &        319337-320065         \\
     2018D1     &        320500-321665        \\
     2018D2     &        321710-322964         \\
     2018D3     &        323363-324420         \\
     2018D4     &        324564-325175        \\
      \end{tabular}
    \caption[Run ranges]{2018 luminosity data periods with run ranges.}
    \label{tab:period_run_ranges}
  \end{center}
\end{table}

In the study under consideration, we have utilized a series of datasets corresponding to the data-taking periods of 2018, namely 2018A, 2018B, 2018C, and 2018D as shown in Table \ref{tab:datasets}. These datasets have been drawn from the Alignment and Calibration (AlCa) project, an integral component of the Compact Muon Solenoid (CMS) experiment conducted at the Large Hadron Collider. The dataset selection includes two subsets denoted as AlCaPCCRandom and AlCaPCCZeroBias. The AlCaPCCRandom dataset comprises of data where trigger is applied on both colliding and non-colliding bunches, thereby providing a holistic and representative view of the whole dataset. On the other hand, the AlCaPCCZeroBias dataset encapsulates events that have passed the trigger system with no bias where trigger is applied on only colliding bunches, thereby serving as an unbiased reference dataset. In terms of processing, the selected datasets have undergone an Express processing pathway. This rapid processing approach, while less detailed than the full reprocessing, provides valuable and timely insights into the data quality and physics performance. The datasets fall within the ALCARECO (ALignment, CALibration, and REConstruction objects) data tier, which specifically encompasses information pertinent to detector alignment and calibration, forming a crucial resource in our analysis. The timestamps associated with these datasets (e.g., $'13Mar2023\_UL2018\_PCC'$) indicate that they have undergone a reprocessing or update post their initial collection in 2018.
%This reprocessing phase enhances the scientific value of these datasets, by incorporating improved calibrations and alignment, and updates to the data reconstruction algorithms. Consequently, the reprocessed datasets used in this thesis afford a more accurate and comprehensive representation of the physics events under investigation.

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{}c@{\hspace{0.5cm}}p{6.5cm}p{6.5cm}@{}}
    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\
    2018A & /AlCaLumiPixels/Run2018A-\newline AlCaPCCRandom-15Apr2023\_UL2018\_\newline 315252\_316062\_PCCRandom\_-v1/ALCARECO, \newline /StreamALCALUMIPIXELSEXPRESS/\newline Run2018A-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018A-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018B & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018C & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018D & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
  \end{tabular}
  \caption[PCC datasets]{Datasets used for studying performance of PCC luminometer \cite{CERNDAS}}
  \label{tab:datasets}
\end{table}

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{}c@{\hspace{0.5cm}}p{6.5cm}p{6.5cm}@{}}
    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\[1em]
    2018A & /AlCaLumiPixels/Run2018A-\newline AlCaPCCRandom-15Apr2023\_UL2018\_\newline 315252\_316062\_PCCRandom\_-v1/ALCARECO, \newline /StreamALCALUMIPIXELSEXPRESS/\newline Run2018A-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018A-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
    2018B & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
    2018C & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
    2018D & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
  \end{tabular}
  \caption{Datasets used for studying performance of PCC luminometer}
  \label{tab:datasets}
\end{table}

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{}c@{\hspace{1cm}}p{5.5cm}p{5.5cm}@{}}
    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\
    2018A & \begin{tabular}{@{}p{5.5cm}@{}}/AlCaLumiPixels/Run2018A-AlCaPCCRandom-15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO, \\ /StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO\end{tabular} & /AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018B & /StreamALCALUMIPIXELSEXPRESS/Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018C & /StreamALCALUMIPIXELSEXPRESS/Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018D & /StreamALCALUMIPIXELSEXPRESS/Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO \\
  \end{tabular}
  \caption{Datasets used for studying performance of PCC luminometer}
  \label{tab:datasets}
\end{table}

%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}

\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}}
%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}

@@

\item $15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1$: This part represents the processing version, date, and run range of the dataset. "15Apr2023" is the date when this specific version of the dataset was created. "UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis. The numbers $"315252_316062"$ represent the range of run numbers included in the dataset. $"PCCRandom_"$ is a reference to the Pixel Cluster Counting method used for luminosity measurement and the random trigger. "v1" denotes the version number of this processed dataset.

@@

%$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$

\textbf{\url{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}}

@@

%$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$

\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO}}

@@

%$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$

\textbf{\url{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}}

@@

The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during

@@

To measure the luminosity using the pixel detector, pixel cluster count is studied for each module, where a module consists of a number of pixels arranged in a grid. The number of pixel clusters recorded in each module per unit time is proportional to the instantaneous luminosity of the collider. To implement PCC method, the pixel detector is operated in an integrated mode, where the detector is read out at a fixed time interval called a "lumi section". During each lumi section, the number of pixel clusters produced in each module is recorded, the rate of pixel clusters and visible cross section of the detector is used to determine the instantaneous luminosity of the collider. PCC data is reprocessed, a procedure that involves the re-analysis of the data using refined or updated algorithms, calibrations, or detector conditions.

\newpage
The purpose of reprocessing can be multifold:

\item Improved Algorithms or Calibration: As experiments progress, there can be improvements in algorithms or calibration techniques used to process the raw data. This can lead to a more accurate or efficient representation of the collected data. Reprocessing allows these improvements to be applied to previously collected data.

\item Changes in Detector Conditions: Detector conditions might change over time due to factors like aging or upgrades. These changes can affect the interpretation of the data. By reprocessing, the data can be reinterpreted to account for these changes.

\item Discovery of Issues or Errors: Sometimes, errors or issues in the original data processing might be discovered. Reprocessing the data allows these errors to be corrected.

In the context of PCC data, reprocessing can lead to a more accurate luminosity measurement, which in turn can affect the interpretation of the physics results derived from the LHC data. The luminosity measurement is crucial because it is directly linked to the determination of cross-sections, a fundamental quantity in the interpretation of the outcomes of high-energy particle physics experiments.

CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets. Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section. Random trigger PCC dataset is reprocessed with new module vetolist to obtain afterglow corrections with improved module stability selections. Zero bias dataset is reprocessed after applying afterglow corrections using same module vetolist with more stringent selections on module stability to obtain PCC luminosity.

@@

\item CMSSW: The CMS Software (CMSSW) is a comprehensive software framework developed for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. CMSSW is used for the simulation, processing, and analysis of data collected by the CMS detector. It is designed to handle various tasks, from the generation of simulated events to the reconstruction of raw detector data, calibration, and high-level analysis. CMSSW is composed of several interconnected components and follows a modular architecture to promote flexibility, reusability, and maintainability. Some key aspects of CMSSW include, Event Data Model (EDM): The EDM serves as the foundation of CMSSW, defining the structure and organization of data objects, such as particle candidates, detector hits, and reconstructed vertices. It is designed to handle the storage, retrieval, and manipulation of these objects efficiently. The CMSSW framework is responsible for the management of software modules, the flow of data between modules, and the execution of the necessary tasks. It also handles the scheduling of tasks and the parallelization of processes, enabling efficient use of computing resources. Modules: CMSSW is built upon a collection of software modules, each responsible for a specific task, such as event generation, detector simulation, reconstruction, or analysis. These modules can be combined and customized to create a complete processing chain for a given use case. The software includes a detailed description of the CMS detector geometry, material properties, and readout electronics. This information is used during the simulation and reconstruction processes to accurately model the detector's response to particles. 
Simulation: CMSSW integrates several external tools and libraries, such as the GEANT4 toolkit, to simulate the passage of particles through the CMS detector. This includes the interactions of particles with the detector material, the production of secondary particles, and the generation of detector signals. Reconstruction: The reconstruction algorithms in CMSSW process the raw detector data, converting it into meaningful physics objects, such as tracks, calorimeter clusters, and particle candidates. These algorithms use a variety of techniques, including pattern recognition, clustering, and fitting, to extract the relevant information from the detector signals. CMSSW includes tools for the calibration of detector components and the alignment of the detector geometry. These tasks are crucial for ensuring the accurate reconstruction of physics objects and the extraction of meaningful results from the data. Analysis: The software provides a rich set of high-level analysis tools and libraries, enabling researchers to perform a wide range of physics analyses, from searches for new particles to precision measurements of Standard Model processes. Data storage and management: CMSSW uses the ROOT data format for the storage and management of data objects. ROOT is a powerful and flexible data storage and processing framework developed at CERN, which provides efficient data handling, advanced statistical analysis tools, and extensive data visualization capabilities \cite{CMSWorkBook}.

@@

\item Brilcalc: The brilcalc tool is a software package designed to calculate and analyze luminosity data for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. Luminosity is a crucial parameter in high-energy physics experiments like CMS, as it measures the rate of collisions in a particle accelerator and directly affects the statistical significance of experimental results. Brilcalc serves as a command-line interface (CLI) tool, which allows users to extract, manipulate, and visualize luminosity data from the CMS experiment. It is built upon the BRIL (Beam Radiation Instrumentation and Luminosity) project, which is responsible for the development and maintenance of beam monitoring and luminosity measurement systems at the CMS experiment. Users can extract luminosity data for a specific data-taking period or data range from the CMS database. The data can be filtered by various criteria, such as run number, fill number, and data-taking conditions. Data manipulation: The tool offers the capability to process and manipulate the extracted luminosity data. Users can perform operations such as unit conversion, data scaling, and data normalization to make the data suitable for further analysis. Brilcalc allows users to perform basic statistical analyses on the luminosity data, such as calculating integrated luminosity, average luminosity, and instantaneous luminosity. These analyses help physicists understand the performance of the CMS detector and plan future data-taking strategies. The tool can generate plots and graphs to visualize the luminosity data, making it easier for researchers to interpret the results and identify trends or anomalies. Brilcalc is designed to be extensible, allowing users to develop custom plugins and scripts for advanced data analysis and visualization tasks \cite{CMSLuminosityCalculationGuide}.

\item CERN ROOT: The ROOT data analysis framework, developed by CERN, is widely used in high-energy physics experiments, including CMS. ROOT offers a rich set of tools for data processing, statistical analysis, and visualization. In the context of PCC luminosity measurement, ROOT is employed to analyze and process the output data from CMSSW, perform statistical analyses, and generate plots for data visualization \cite{ROOT}.

@@

\item DASgoclient: The DASgoclient is a command-line interface for the CMS Data Aggregation System (DAS). It offers researchers an alternative method for accessing various CMS data services without using the web-based DAS interface. The DASgoclient allows users to query and retrieve data in a more scriptable and automated manner, making it an essential tool for managing datasets and streamlining the data retrieval process for PCC luminosity measurement.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
\caption{%                                                                                                                                                                                                      
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_L0_veto}
\end{figure}

@@

\item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.

@@

\item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis. Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurement.

By carefully analyzing the module weights and excluding the bad modules from the analysis, the instabilities in PCC luminosity measurement can be minimized. This process ensures that the data used for luminosity measurement is of high quality and can produce precise results.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight.png}
\caption[Steps involved to obtain module weights]{%
   Method to obtain module weights as a function of lumi section for categorizing good and bad modules. X profile of TH2F histogram (module PCC/total PCC per lumi section) is obtained. X profile is then filled in a TGraph after removing points with error $>$ 0.05. TGraph is normalized with the mean of Y projection of TH2F histogram to obtain module stability profile.
}
\label{fig:mod_weight}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules.png}
\caption[Good and bad module weights]{%
   Change in normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large RMS/mean values are used to make module veto list.
}
\label{fig:goodbadmodules}
\end{figure}

\newpage
The module veto list is a list of detector modules that are excluded from the analysis of data due to their known or suspected high rate of background events or other issues that could affect the accuracy of the measurement. The inclusion of certain modules in the veto list is based on various factors, including:

\item Manufacturing defects: Defects in the silicon material or issues during the manufacturing process can result in poorly performing pixel modules. These defects may not be immediately evident but can become more pronounced overtime.

\item Contamination or environmental factors: Contamination of the pixel modules by dust, moisture, or other substances can affect their performance or cause them to fail. Similarly, external environmental factors, such as magneticfields or vibrations, can impact the operation of the pixel modules.

Module veto list consisting of bad modules is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,

@@

\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut}. % and \ref{fig:f_it}.

\item All barrel layer 1 modules are removed as these modules are significantly affected by dynamic inefficiency effects, where the hit efficiency decreases at higher instantaneous luminosity due to the readout chip not being able to process all of the hits.

\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile. Modules with significantly large RMS/mean are removed with this loose selection as shown in Fig. \ref{fig:outliermodules}.

\item Module stability is re-evaluated based on RMS/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig. \ref{fig:sec_it_cut}.                                                      
\end{itemize}

@@

\item Period B module vetolist is applied to these periods to determine remaining bad modules.

@@

\item module weight comparisons between period B and these periods is done and modules with more than 3 sigma change in module weights are removed as shown in %Fig. \ref{fig:mod_w_com} and
  Fig \ref{fig:mod_w_com_1}.                                                                              
\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
\caption[Selection to remove low statistics lumi sections]{%
 Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC shown by the red line is applied to remove low statistics lumi sections.
}
\label{fig:PCC_cut}
\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration.png}
%\caption{%
%   A loose cut of 7\% is applied on rms/mean values of module stability profile to remove outlier modules.
%}
%\label{fig:f_it}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/cut_selection.png}
\caption[First iteration to remove outlier modules]{%
   RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
}
\label{fig:outliermodules}
\end{figure}
